\documentclass{article}

\usepackage{fullpage,url}
\usepackage{csquotes}
\usepackage[british]{babel}
\usepackage{booktabs}
\usepackage[cleanlook,british]{isodate}

\usepackage[sorting=ynt]{biblatex}  % sort by year
\addbibresource{cvbib.bib}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	citecolor=green,
	urlcolor=black
}

\usepackage{enumitem}
\setlist[itemize]{leftmargin=0pt, itemsep=3pt plus 1pt minus 1pt}

\usepackage{datenumber}
\usepackage{fp}
% age calculation
\newcounter{birthdate}
\newcounter{todaydate}
\setmydatenumber{birthdate}{1992}{11}{02}
\setmydatenumber{todaydate}{\the\year}{\the\month}{\the\day}
\FPsub\diff{\thetodaydate}{\thebirthdate}
\FPdiv\myage{\diff}{365.2425}
\FPtrunc\myyears{\myage}{0}

\newcommand{\email}[1]{\href{mailto:#1}{\texttt{#1}}}

\author{Liam Baker}
\title{Curriculum Vitae}
\date{\today}


\begin{document} \maketitle


\section{Personal Information}
\begin{center} \begin{tabular}{ll}
	Full name: 								& Liam Bradwin Baker \\
	Age: 											& \myyears~years \\
	Date of Birth:						& 2 November 1992 \\
	Gender: 									& Male \\
	Citizenship:							& South Africa \\
	Current occupation:				& Mathematics Lecturer \& Researcher \\
	Contact numbers:					& \href{tel:+27842789447}{+27 84 278 9447} (personal) \\
														& \href{tel:+27218083286}{+27 21 808 3286} (work) \\
														& \href{tel:+27605074681}{+27 69 161 9804} (backup) \\
	Email:										& \email{bakerbakura@gmail.com} (personal)\\
														& \email{liambaker@sun.ac.za} (work) \\
	Languages:								& English, \footnotesize{Afrikaans}, \tiny{French} \\
	Programming Languages:		& Python, Mathematica, R, git, \LaTeX, SQL \\
														& \footnotesize{bash, SageMath, Java} \\
\end{tabular} \end{center}


\section{Educational History}
\renewcommand{\t}{\hspace{0.4cm}}
\begin{center} \begin{tabular}{lp{0.6\textwidth}l}
\toprule
Primary:
& Duneside Primary School (Grade 1)														& 1999 \\
\cmidrule{2-3}
& Imperial Primary School (Grades 2--7)												& 2000--2005 \\
\midrule

Secondary:
& \href{http://www.mondalehs.co.za/}{Mondale High School}			& 2006--2009 \\
& \t Matric certificate received								 							& \t December 2009 \\
\midrule

Tertiary:
& \href{http://www.uct.ac.za/}{University of Cape Town (UCT)} & 2010--2013 \\
& \t BSc (Maths, Applied Maths) with distinction received			& \t December 2012 \\
& \t BSc (Hons) (Mathematics) first class received 						& \t December 2013 \\
\cmidrule{2-3}
& \href{http://www.sun.ac.za/}{Stellenbosch University (SU)}	& 2014--2015 \\
& \t MSc (Mathematics) cum laude received								 			& \t December 2015 \\
& \multicolumn{2}{l}{\t \t \small{Thesis title: \textit{Analytic methods in combinatorial number theory}}} \\
& \t \t \small{Supervisor: Prof Stephan Wagner} \\
\cmidrule{2-3}
& \href{http://www.sun.ac.za/}{Stellenbosch University (SU)}	& 2018--2020 \\
& \t PhD (Mathematics) received 															& \t April 2020 \\
& \multicolumn{2}{l}{\t \t \small{Thesis title: \textit{Drinfeld modular forms of higher rank from a lattice-oriented point of view}}} \\
& \multicolumn{2}{l}{\t \t \small{Supervisor: Dr Dirk Basson} \t \small{Co-supervisor: Prof Florian Breuer}} \\
\bottomrule
\end{tabular} \end{center}


\clearpage
\section{Employment History}
\begin{itemize}
	\item Self-employed as a private tutor for secondary and tertiary students from 2007 to 2014.
	\item Employed by UCT's \href{http://www.math.uct.ac.za/}{Department of Mathematics and Applied Mathematics} as a Mathematics Tutor from February 2012 to November 2013.
	\item Employed by SU's \href{http://www.sun.ac.za/english/faculty/science/Mathematics}{Department of Mathematical Sciences} as a Tutor from February to November 2015.
	\item Employed by \href{https://www.standardbank.co.za/}{The Standard Bank of South Africa} as a Data Analyst from February to October 2016.
	\item Employed by \href{http://www.isaziconsulting.co.za}{Isazi Consulting (Pty) Ltd.} as a Data Scientist from November 2016 to January 2018.
	\item Employed by SU's \href{http://www.sun.ac.za/english/faculty/science/Mathematics}{Department of Mathematical Sciences} as a Contract Lecturer from April to November 2018, lecturing two large first-year engineering mathematics courses.
	\item Employed by \href{http://www.isaziconsulting.co.za}{Isazi Consulting (Pty) Ltd.} as a Data Scientist from November 2019 to July 2020.
	\item Employed by SU's \href{http://www.sun.ac.za/english/faculty/science/Mathematics}{Department of Mathematical Sciences} as a Lecturer from July 2020.
\end{itemize}


\section{Academic Achievements and Participation}

\subsection{Participation in mathematical competitions}
\begin{itemize}
	\item Placed 11th, 3rd, 1st, and 2nd in the \href{http://www.mth.uct.ac.za/competition/}{UCT Mathematics Competition} in 2006, 2007, 2008 and 2009.
	\item Placed 4th and 3rd in the \href{http://www.samf.ac.za/sa-mathematics-olympiad}{South African Mathematics Olympiad (SAMO)} in 2008 and 2009 respectively.
	\item Represented South Africa at the 2008 \href{https://www.africamathunion.org/AMU-pamo-official.php}{Pan African Mathematical Olympiad (PAMO)} held in Benin, winning a silver medal and placing 5th.
	\item Represented South Africa at the 2008 \href{http://imo-official.org/}{International Mathematical Olympiad (IMO)} held in Madrid, Spain, achieving an Honourable Mention.
	\item Represented South Africa at the 2009 IMO held in Bremen, Germany, winning a bronze medal.
	\item Represented UCT at the \href{http://www.imc-math.org.uk/index.php?year=2013}{20th International Mathematics Competition for Students} (IMC) held in Blagoevgrad, Bulgaria in 2013, winning a First Prize and placing 33rd of 321 contestants.
	\item Participated in the IMC in 2014, 2015, 2018 and 2019 as Team Leader for SU's and UCT's teams, and in 2021 as one of the Team Leaders for the combined South African team.
	\item Participated in the PAMO in 2015 and 2016 as Team Leader for the South African team, in 2018 as a member of the Problem Committee and a Coordinator (marker), in 2019 as the chair of the Local Organising Committee (and thus also a member of the Supervising Committee), and in 2021, 2022, 2023, 2024, and 2025 as a member of the Problem Committee and Supervising Committee.
	\item Was the Vice-chairperson of the Local Organising Committee for the 2024 PAMO.
	\item Participated in the IMO in 2014 and 2025 as a Problem Coordinator and in 2017, 2018, 2019, 2020, 2021, 2022, and 2023 as Team Leader for the South African team.
	\item Participated in the \href{http://www.simonmarais.org/}{Simon Marais Mathematics Competition (SMMC)} in 2021, 2022, 2023, 2024, and 2025 as a member of the Problem Committee.
\end{itemize}

\newpage
\subsection{Bursaries, scholarships and fellowships}
\begin{itemize}
	\item Recipient of a Science Entrance Scholarship and a Vice-Chancellor's Scholarship from UCT in 2010.
	\item Recipient of a bursary from the \href{http://www.sasolinzalofoundation.org.za/}{Sasol Inzalo Foundation} in the years 2011, 2012 and 2013.
	\item Recipient of a Science Faculty Scholarship from UCT in the years 2011 and 2012.
	\item Recipient of a Jacob Burlak Memorial Scholarship from UCT in 2011.
	\item Recipient of a \href{http://www.mmuf.org/}{Mellon Mays Undergraduate Fellowship} in the 2012/2013 period.
	\item Recipient of a Postgraduate Merit bursary from Stellenbosch University in 2014.
	\item Recipient of a bursary from the Standard Bank 150 Programme in 2014 and 2015.
	\item Recipient of a bursary from the \href{http://thecrossleyfoundation.co.za/}{Harry Crossley Foundation} in 2018 and 2019.
	\item Recipient of a bursary from the \href{https://www.wits.ac.za/coe-mass/}{Centre of Excellence in Mathematical and Statistical Sciences} in 2019.
\end{itemize}

\subsection{Conferences, workshops and summer schools}
\begin{itemize}
	\item Participated in the inaugural \href{http://math.jacobs-university.de/summerschool/2011}{International Mathematical Summer School for Students} in 2011.
	\item Participated in a Summer Research Colloquium held at Williams College in the US in 2012 focussing on how to conduct research, as part of the aforementioned Mellon Mays Undergraduate Fellowship.
	\item Presented work at the Mellon Mays Undergraduate Fellowship Regional Workshop in September 2013.
	\item Participated in the \href{http://www.heidelberg-laureate-forum.org/event_2014/}{2nd Heidelberg Laureate Forum} held in Heidelberg, Germany in 2014.
	\item Participated in the \href{http://www.unisa.ac.za/Default.asp?Cmd=ViewContent&ContentID=96795}{57th Annual Conference of the South African Mathematical Society} in 2014.
	\item Participated in the \href{http://www.aims.ac.za/en/research-centre/workshops-conferences/past/aims-stellenbosch-university-number-theory-conference-19-23-january-2015}{AIMS-Stellenbosch University Number Theory Conference}, 19--23 January 2015.
	\item Participated in the \href{http://www.impa.br/opencms/pt/eventos/store/evento_1504}{inaugural International Conference in Number Theory and Physics} held at IMPA in Rio de Janeiro, Brazil from 15--26 June 2015.
	\item Participated in the conference \href{https://dmvpisa2018.wordpress.com/}{New Developments in the Theory of Modular Forms over Function Fields} in Pisa, Italy in November 2018.
	\item Presented work at the AIMS-Stellenbosch University Number Theory Conference, 14--18 January 2019.
	\item Presented work at the Drakensberg Maths Conference for Emerging Researchers, 9--14 January 2022.
	\item Presented work while being a Member at the Institute for Advanced Studies in Princeton from 21 September--21 December 2024.
\end{itemize}

\subsection{Other}
\begin{itemize}
	\item Won class medals at UCT for MAM1000W (Mathematics 1), MAM1019H (Fundamentals of Mathematics), and MAM1043H (Modelling and Applied Computing) in 2010, MAM2000W (Mathematics 2) in 2011, and MAM3000W (Mathematics 3) in 2012, with final marks of 99\%, 100\%, 102\%, 100\%, and 100\% respectively.
	\item Submitted a problem for use in the 2012 IMO, which was used as Problem 4. This is the first ever IMO problem which was submitted from an African country.
	\item Submitted a problem for use in the 2019 IMO, which was used as Problem 1. This is the third ever IMO problem which was submitted from an African country.
	\item Received the S2A3 medal in 2015 from the \href{http://s2a3.org.za/joomla/index.php}{Southern African Association for the Advancement of Science} for the best MSc thesis at Stellenbosch University for that year.
	\item Appeared on Cape Town TV and CCFM for public engagement regarding mathematics competitions.
\end{itemize}


% \clearpage
\section{Service}
\begin{itemize}
	\item Since December 2011 I have volunteered as a coach at various training and selection camps organised by the \href{http://www.samf.ac.za/}{South African Mathematics Foundation (SAMF)} for the purpose of identifying and training teams to represent South Africa at the International Mathematical Olympiad (IMO) and Pan African Mathematical Olympiad (PAMO).
	\item From January 2012 I have volunteered at Hillsong Church South Africa, at the Century City campus from January 2012 to March 2013, at the Mitchells Plain campus from June 2012 to March 2015, at the Johannesburg campus from February 2016 to January 2018 and at the Stellenbosch campus from March 2018. I have also led a team of volunteers at Mitchells Plain every Sunday from February 2014 to July 2015, and currently at the Stellenbosch campus from March 2018.
	\item Since September 2014 I have served as a member of the Senior Third Round committee for the SAMO. The responsibility of this committee each year is to set and mark the Senior Third Round papers.
	\item I have served as a member of the African Mathematical Union's \href{http://www.africamathunion.org/amu-pamoc/}{Commission for the PAMO} (AMUPAMOC) representing Southern Africa since August 2017.
	\item I have served as the regional representative for Africa on the \href{http://www.wfnmc.org/}{World Federation of National Mathematics Competitions} since August 2018.
\end{itemize}


\section{Character and Academic References}
\begin{center} \begin{tabular}{llll}
	\toprule
	Name						& Institution							& Relation					& Email address \\
	\midrule
	Dr D Basson			& Stellenbosch University	& PhD supervisor		& \email{djbasson@sun.ac.za} \\
	Prof F Breuer		& University of Newcastle	& PhD co-supervisor	& \email{Florian.Breuer@newcastle.edu.au} \\
	% Prof A Solarin	& National Math. Centre		& AMUPAMOC Chair		& \email{asolarin2002@yahoo.com} \\
	Prof S Wagner		& Uppsala University			& MSc supervisor		& \email{stephan.wagner@math.uu.se} \\
	Ps D Webster	& Hillsong Church Africa	& Pastor						& \email{david.webster@hillsong.co.za} \\
	\bottomrule
\end{tabular} \end{center}


\vfill
\nocite{*}
\printbibliography[title=Publications]

\end{document}