\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage{url}
\usepackage{csquotes}
\usepackage{hyperref}

\author{Liam Baker}
\title{Short Curriculum Vitae}
\date{\vspace{-24pt}}


\begin{document} \maketitle \thispagestyle{empty}

\section{Personal Information} \begin{center} \begin{tabular}{ll}

	Full name: 					    	& Liam Bradwin Baker \\
	Date of Birth:					  & 2 November 1992 \\
	Gender: 							    & Male \\
	Contact number: 				  & +27 84 278 9447 \\
	Email:							      & \href{mailto:bakerbakura@gmail.com}{\texttt{bakerbakura@gmail.com}} \\
	Languages:						    & English, \footnotesize{Afrikaans}, \tiny{French} \\ 

\end{tabular} \end{center}


\section{Selected Positions and Achievements} \begin{itemize}

  \item Highest degree received: \href{http://hdl.handle.net/10019.1/98017}{MSc (Mathematics)} received cum laude at \href{http://www.sun.ac.za}{Stellenbosch University} (SU) in December 2015.
  \item Received BSc (Hons) (Mathematics) first class at the \href{http://www.uct.ac.za}{University of Cape Town} (UCT) in December 2013.
  \item Employed by \href{http://www.isaziconsulting.co.za}{Isazi Consulting (Pty) Ltd.} as a Data Scientist from November 2016 to January 2018.
	\item Employed by SU's \href{http://www.sun.ac.za/english/faculty/science/Mathematics}{Department of Mathematical Sciences} as a Contract Lecturer from April to November 2018, lecturing two large first-year engineering mathematics courses.
  \item Employed since December 2011 as a coach at various training and selection camps organised by the \href{http://www.samf.ac.za/}{South African Mathematics Foundation} (SAMF) for the purpose of identifying and training teams  to represent South Africa at the \href{http://www.imo-official.org/}{International Mathematical Olympiad} (IMO) and \href{http://www.pamo-official.org/}{Pan African Mathematical Olympiad} (PAMO), and also as a member of the Senior Third Round committee for the \href{http://www.samf.ac.za/sa-mathematics-olympiad}{South African Mathematics Olympiad (SAMO)}.
  \item Represented South Africa at the \href{http://www.imo-official.org/year_info.aspx?year=2009}{2009 IMO} held in Germany, winning a bronze medal.
	\item Represented UCT at the \href{http://www.imc-math.org.uk/index.php?year=2013}{20th International Mathematics Competition for Students} (IMC) held in Blagoevgrad, Bulgaria in 2013, winning a First Prize and placing 33rd of 321 contestants.
	\item Participated in the IMC in 2014, 2015 and 2018 as Team Leader for SU's team and UCT's team; in the PAMO in 2015 and 2016 as Team Leader for the South African team, in 2018 as a member of the Problem Committee and a Coordinator (marker), and in 2019 as the chairperson of the Local Organising Committee (and thus also a member of the Supervising Committee); and in the IMO in 2014 as a Problem Coordinator and in 2017 and 2018 as Team Leader for the South African team.
	\item Recipient of various bursaries for tertiary study, including a Vice-Chancellor's Scholarship from UCT, the \href{http://www.mmuf.org/}{Mellon Mays Undergraduate Fellowship} and bursaries from the \href{https://www.sasol.com/sustainability/social-investment/inzalo-foundation}{Sasol Inzalo Foundation}, the Standard Bank 150 Programme, the Harry Crossley Foundation and the \href{https://www.wits.ac.za/coe-mass/}{Centre of Excellence in Mathematical and Statistical Sciences}.
	\item Participated in the \href{http://www.heidelberg-laureate-forum.org/event_2014/}{2nd Heidelberg Laureate Forum} held in Heidelberg, Germany in 2014.
  \item Submitted a problem for use in the 2012 IMO, which was accepted and used as Problem 4. Is the first African to have had a problem accepted for the IMO.
	\item Received the S2A3 medal in 2015 from the \href{http://s2a3.org.za/joomla/index.php}{Southern African Association for the Advancement of Science} for the best MSc thesis at Stellenbosch University for that year.
	\item From January 2012 has volunteered at \href{http://www.hillsong.co.za}{Hillsong Church South Africa}: at the Century City campus from January 2012 to March 2013, at the Mitchells Plain campus from June 2012 to March 2015, at the Johannesburg campus from February 2016 to January 2018 and at the Stellenbosch campus from March 2018. Has also led a team of volunteers at the Mitchells Plain campus every Sunday from February 2014 to July 2015, and currently at the Stellenbosch campus from March 2018.

\end{itemize}

\end{document}
